---
title: "Assignment_01"
author: "Thilokesh"
date: "2025-10-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Create A Dataframe
Performed the following Steps in Rstudio Console:

- animals = c("Snake","Ostrich","Cat","Spider")
- num_legs = c(0,2,4,8)
- animals_df = data.frame(animals,num_legs)

## 2. Checking and Deleting Objects
- ls() # Lists all the variables in the environment(list of variables by name)
- ?rm  # To get the help document on rm
- rm(num_legs) # Removes the variable from the environment
- ls() # Now only two variables remain.
- rm(list=ls()) # will remove all the variables in the current environment

## 3. Creating a Data Frame in R Scripts
Done in "myFirstRScript.R"

## 4. Creating a Data Frame in R Markdown
- Creating the Data Frame :
```{r Creating the Data Frame}
animals = c("Snake","Ostrich","Cat","Spider")
num_legs = c(0,2,4,8)
animals_df = data.frame(animals,num_legs)
```
- Displaying the Data Frame (echo=FALSE):
```{r Displaying the DataFrame, echo=FALSE}
show(animals_df)
```

## 5. Matrix Operations
- Creating a matrix (include=FALSE)
```{r Creating A Matrix x_vect, include=FALSE}
x_vect = seq(from=12,to=2,by=-2)
```
- Show x_vect that is created above
```{r Show x_vect, echo=FALSE}
x_vect
```
- Converting the previous vector into Matrix X
```{r Converting vector to Matrix X}
X = matrix(data=x_vect,nrow = 2, ncol = 3)
X
```
- Creating a Matrix Y with seq function
```{r Creating a Matrix Y with seq func }
Y = matrix(seq(4), 2, 2)
Y
```
- Creating another Matrix Z 
```{r Creating another Matrix Z}
Z = matrix(seq(4,10,2), 2, 2)
Z
```
- Transposing the Matrix Y and Z
```{r Transposing the Matrix Y and Z}
t(Y)
t(Z)
```
- Commutative operation in Matrix
```{r Commutative operation}
Y+Z
Z+Y
```
- Checking what happens when we do Y*Z
```{r Dot Product}
Y*Z
```
- Computing the proper Matrix Multiplication
```{r Proper Matrix Multiplication}
Y %*% Z
```
- Checking what happens when we try XY? R tries to search for variable XY as it does not understand that by XY we want it to multiply X and Y.
  * Error in h(simpleError(msg, call)) : 
  error in evaluating the argument 'object' in selecting a method for function 'show': object 'XY' not found
- Matrix Inverse ($Y^{-1}$)
```{r Using solve func to compute matrix inverse}
solve(Y)
```
- Computing $Y^{-1}Y$
```{r Y inverse Y}
solve(Y)%*%Y
```
- Computing $Y^{-1}X$
```{r Y Inverse X}
solve(Y)%*%X
```
- Computing $Y^{-1}X$ with out actually calculating $Y^{-1}$
```{r}
solve(Y,X)
```
Explanation:

  * If Y * result = X, then result = Y^-1 * X
  * So solve(Y, X) finds the result that satisfies Y * result = X
  * That result IS Y^-1 * X, but R never actually computes Y^-1

## 6. Creating A Function in R Script
Done in "functions.R"

## 7. Further R Markdown exercises
Done in file "R_Markdown_Exercises.Rmd"

## 8. Version Control with Git.













